PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added a little/much better retro prepan correlation and scatterplots. Added a glad edgi participant filter to every scatterplot

@@

```{r Whole sample Correlation prep chunk}

@@

@@

much_worse_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse")

little_worse_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little worse")

much_worse_little_worse_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" | 
           gad.pandemic_felt_feelings == "A little worse")

@@

much_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_gad)[1]))

little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_gad)[1]))

much_worse_little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_little_worse_gad)[1]))

@@

@@

little_better_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little better")

much_better_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better")

much_better_little_better_gad <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better" | 
           gad.pandemic_felt_feelings == "A little better")

@@

little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_gad)[1]))

much_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_better_gad)[1]))

much_better_little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") + 
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_little_better_gad)[1]))

>>>>

#Create a data set with only the GLAD and EDGI participants
whole_retro_prepan_scatter <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]

#Check that RAMP and NBR has been removed
whole_retro_prepan_scatter %>% 
  freq(Sample)

@@

```{r Little/much worse correlation prep chunk}

@@

#Create a data set with only the GLAD and EDGI participants
little_much_worse_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]

#Check that RAMP and NBR has been removed
little_much_worse_retro_prepan %>% 
  freq(Sample)

@@

much_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse")

little_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little worse")

much_little_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" | 
           gad.pandemic_felt_feelings == "A little worse")

@@

much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_gad_scatter)[1]))

little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_gad_scatter)[1]))

much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_gad_scatter)[1]))

#Little/much better prepan retro correlation

```{r Little/much better correlation prep chunk}

#Create a data set with only the GLAD and EDGI
prepan_retro_dat_better <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]

prepan_retro_dat_better <- prepan_retro_dat_better %>% 
  filter(gad.pandemic_felt_feelings == "A little better" |
           gad.pandemic_felt_feelings == "Much better")

#Check that RAMP and NBR has been removed
prepan_retro_dat_better %>% 
  freq(Sample)

# Calculate correlation matrix on specific columns (variables) from your data frame
prepan_retro.corr.mat_better <- hetcor(
  as.data.frame(prepan_retro_dat_better[,prepan_retro_items]), # Specify the data
  use = "pairwise.complete.obs" # Use all pairwise observations
)

# Print the correlation matrix
print(prepan_retro.corr.mat_better, digits = max(3, getOption("digits") - 3))

# Save the correlations from the correlation matrix in an object
prepan_retro.corr.matrix_better <- as.matrix(prepan_retro.corr.mat_better)

# Save the p values from the correlation matrix in an object
prepan_retro.p.matrix_better <- as.matrix(prepan_retro.corr.mat_better$tests)

res1 <- cor.ci(prepan_retro.corr.matrix_better)
lowci <- cor.plot.upperLowerCi(res1)
lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]

```{r Little/much better correlation matrix of prepan retro sum scores}
corrplot(prepan_retro.corr.matrix_better, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = prepan_retro.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank" # Nonsignificant correlations have no colour
         )

@@

#Create a data set with only the GLAD and EDGI participants
little_much_better_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]

#Check that RAMP and NBR has been removed
little_much_better_retro_prepan %>% 
  freq(Sample)

@@

little_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little better")

much_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better")

much_little_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better" | 
           gad.pandemic_felt_feelings == "A little better")

@@

little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_gad_scatter)[1]))

much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_gad_scatter)[1]))

much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") + 
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))
